A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-04 latex/main.tex

We validated the recombination events in the sc2ts ARG
by running 3SEQ~\cite{Lam2018improved}
on the putative recombinant sequence trios (STAR Methods)\sout{,
and 484 of the 855 (57\%) were classified as recombinant.
Validation status correlates strongly with our QC filter,
with 95\% of the QC-passing recombinants
and 29\% of the QC-failing recombinants
being classified as recombinant.}
.
Of the 855 recombination events identified by sc2ts, 3SEQ verified 57\% of them, rising to 95\% verification among the 354 recombinants that passed our QC filter. 
In addition to 3SEQ, we ran the CovRecomb~\cite{Li2024CovRecomb} 
and rebar recombination detection methods
on the putative recombinant sequences,
summarized in Table~\ref{tab:recombinant_validation}.
CovRecomb has a substantially lower validation rate
at 25\% among the QC-passing recombinants.
This is expected, as CovRecomb is specifically intended
to detect interlineage recombinants
and has previously been shown to be
less sensitive than other methods~\cite{Li2024CovRecomb}.
Rebar validation is intermediate, at 57\% among QC-passing recombinants.
(See also Figures~\ref{fig:recombinant_evidence_cov_recomb},
and \ref{fig:recombinant_evidence_rebar}.)
% We don't talk about RIPPLES results yet as we haven't discussed it, a
% and that would be confusing.

>>>>

We validated the recombination events in the sc2ts ARG
by running 3SEQ~\cite{Lam2018improved}
on the putative recombinant sequence trios (STAR Methods)\sout{,
and 484 of the 855 (57\%) were classified as recombinant.
Validation status correlates strongly with our QC filter,
with 95\% of the QC-passing recombinants
and 29\% of the QC-failing recombinants
being classified as recombinant.}
.
Of the 855 recombination events identified by sc2ts, 3SEQ verified 57\% of them, rising to 95\% verification among the 354 recombinants that passed our QC filter. 
In addition to 3SEQ, we ran the CovRecomb~\cite{Li2024CovRecomb} 
and rebar (\url{https://github.com/phac-nml/rebar}) recombination detection methods
on the putative recombinant sequences,
summarized in Table~\ref{tab:recombinant_validation}.
CovRecomb has a substantially lower validation rate
at 25\% among the QC-passing recombinants.
This is expected, as CovRecomb is specifically intended
to detect interlineage recombinants
and has previously been shown to be
less sensitive than other methods~\cite{Li2024CovRecomb}.
Rebar validation is intermediate, at 57\% among QC-passing recombinants.
(See also Figures~\ref{fig:recombinant_evidence_cov_recomb},
and \ref{fig:recombinant_evidence_rebar}.)
% We don't talk about RIPPLES results yet as we haven't discussed it, a
% and that would be confusing.
